---
title: "Workshop Report"
format: html
editor: visual
---

## Collaborators

| Name | Institution |
|------|-------------|
|      |             |
|      |             |
|      |             |
|      |             |

------------------------------------------------------------------------

## Introduction

*Describe the topic of your report here. What question are you trying to answer? Why is it relevant?*

------------------------------------------------------------------------

## Data

*Briefly describe the dataset you are using: where it comes from, how many observations it has, and what variables are included.*

```{r}
# Load your data here
# Example: data <- read.csv("your_file.csv")

```

*Add a short description of the variables that are most relevant to your analysis.*

------------------------------------------------------------------------

## Analysis

*Explain the method or approach you are using to analyse the data.*

```{r}
# Write your analysis code here

```

------------------------------------------------------------------------

## Results

*Summarise what you found. You can reference numbers, tables, or plots produced above.*

```{r}
# Add any additional plots or tables here

```

------------------------------------------------------------------------

## Conclusions

*What do the results mean? What are the limitations of your analysis? What would you do next?*

------------------------------------------------------------------------

## References

*List any sources, datasets, or packages you used.*
